Parameter space representation of Pareto set

### 2013-09-26 algorithm.tex
Cleaning lists

\paragraph{START CONDITION}
\begin{itemize}
\item $\mathcal{R}_{0}=\left\{ P_{1}\times\dots\times P_{n}\right\} $,
i.e. era $0$ has only one region that is the whole parameter space.
A random set $test_{0}$ of $K$ configurations is evaluated. The
Pareto set $\mathscr{P}_{0}=\mathscr{P}\left(test_{0}\right)$ is
calculated (see def \ref{pers02.def:Pareto-set} for the definition
of the operator $\mathscr{P}_{i}$ over a set)
\end{itemize}

\paragraph{ITERATION RULES}

@@

\begin{enumerate}
\item high innovation regions 
\[
\mathcal{R}_{i,h}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)>\alpha\cdot is_{av,i-1}\right\} 
\]
 where $\alpha$ is a constant defined by the designer (for example
$\alpha=1.2$). Each $R\in\mathcal{R}_{i,h}$ is split in $\mathcal{R}^{R}$
(as stated in def \ref{pers02.def:Splitting-a-region})
\item low innovation regions 
\[
\mathcal{R}_{i,l}=\left\{ \left.R\in\mathcal{R}_{i}\right|0<is\left(R\right)\le\alpha\cdot is_{av,i-1}\right\} 
\]
They are not changed.
\item no innovation regions 
\[
\mathcal{R}_{i,n}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)=0\right\} 
\]

\end{enumerate}
\item Disjoint couples of contiguous regions $\left(R_{1},R_{2}\right)$,
with $R_{1},R_{2}\in\mathcal{R}_{i,n}$ are selected. The set of this
couples is indicated as $\mathcal{C}$. The couples of regions are
merged:
\[
\forall\left(R_{1},R_{2}\right)\in\mathcal{C}\Rightarrow R=R_{1}+R_{2}
\]
 (see def \ref{pers02.def:Merging-regions})
\item The set of regions $\mathcal{R}_{i+1}$ for the following era is defined
as:
\[
\mathcal{R}_{i+1}=
\]
\[
=\left(\bigcup_{R\in\mathcal{R}_{i,h}}\mathcal{R}^{R}\right)\cup\mathcal{R}_{i,l}\cup
\]
\[
\cup\left(\mathcal{R}_{i,n}\setminus\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left\{ R_{1},R_{2}\right\} \right)\cup
\]
\[
\cup\left(\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left(R_{1}+R_{2}\right)\right)
\]

@@

\paragraph{TERMINATION CONDITION}
\begin{itemize}
\item The algorithm terminates at step $k$ if
\[
is_{TOT,k},is_{TOT,k-1},\dots,is_{TOT,k-\beta}\le\gamma\cdot is_{TOT,k-\left(\beta-1\right)}
\]
 where $\beta$ and $\gamma$ are selected by the experimenter (see
remark \ref{rem:termination}).\end{itemize}
\begin{rem}
\label{pers02.rem:smaller_regions}The rule \ref{pers02.enu:K} of
the iteration rules says that the smaller is a region, the more ``crowded''
it is. It means that configurations in smaller regions are evaluated
with more ``attention'' (see figure \ref{pers02.fig:small_and_big}).

>>>>

\subsection{Start Condition}
$\mathcal{R}_{0}=\left\{ P_{1}\times\dots\times P_{n}\right\} $,
i.e. era $0$ has only one region that is the whole parameter space.
A random set $test_{0}$ of $K$ configurations is evaluated. The
Pareto set $\mathscr{P}_{0}=\mathscr{P}\left(test_{0}\right)$ is
calculated (see def \ref{pers02.def:Pareto-set} for the definition
of the operator $\mathscr{P}_{i}$ over a set)

\subsection{Iteration Rules}

@@

\begin{enumerate}
\item high innovation regions 
\[
\mathcal{R}_{i,h}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)>\alpha\cdot is_{av,i-1}\right\} 
\]
 where $\alpha$ is a constant defined by the designer (for example
$\alpha=1.2$). Each $R\in\mathcal{R}_{i,h}$ is split in $\mathcal{R}^{R}$
(as stated in def \ref{pers02.def:Splitting-a-region})
\item low innovation regions 
\[
\mathcal{R}_{i,l}=\left\{ \left.R\in\mathcal{R}_{i}\right|0<is\left(R\right)\le\alpha\cdot is_{av,i-1}\right\} 
\]
They are not changed.
\item no innovation regions 
\[
\mathcal{R}_{i,n}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)=0\right\} 
\]
\end{enumerate}

\item Disjoint couples of contiguous regions $\left(R_{1},R_{2}\right)$,
with $R_{1},R_{2}\in\mathcal{R}_{i,n}$ are selected. The set of this
couples is indicated as $\mathcal{C}$. The couples of regions are
merged:
\[
\forall\left(R_{1},R_{2}\right)\in\mathcal{C}\Rightarrow R=R_{1}+R_{2}
\]
 (see def \ref{pers02.def:Merging-regions})
\item The set of regions $\mathcal{R}_{i+1}$ for the following era is defined
as:
\[
\mathcal{R}_{i+1}=
\]
\[
=\left(\bigcup_{R\in\mathcal{R}_{i,h}}\mathcal{R}^{R}\right)\cup\mathcal{R}_{i,l}\cup
\]
\[
\cup\left(\mathcal{R}_{i,n}\setminus\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left\{ R_{1},R_{2}\right\} \right)\cup
\]
\[
\cup\left(\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left(R_{1}+R_{2}\right)\right)
\]

@@

\subsection{Termination Condition}
The algorithm terminates at step $k$ if
\[
is_{TOT,k},is_{TOT,k-1},\dots,is_{TOT,k-\beta}\le\gamma\cdot is_{TOT,k-\left(\beta-1\right)}
\]
 where $\beta$ and $\gamma$ are selected by the experimenter (see
remark \ref{rem:termination}).
\begin{rem}
\label{pers02.rem:smaller_regions}The rule \ref{pers02.enu:K} of
the iteration rules says that the smaller is a region, the more ``crowded''
it is. It means that configurations in smaller regions are evaluated
with more ``attention'' (see figure \ref{pers02.fig:small_and_big}).
